---
title: "Midterm"
output: html_notebook
---
Step 1: First we want import the IMDB Data from the csv & attach it to make it easier to work with

```{r}
imdb = read.csv("data_final.csv")
attach(imdb)
```

Step 2: Get a better look at the data overall
```{r}
#head(imdb)
#str(imdb) 
#We can see that the data is made up of integers, factors and a dummy variable for genre. Nice!
#We also have NA values that we need to deal with
```

Step 3: We can remove some unecessary columns: language, country, movie_imdb_link, plot_keywords, color, genres, plot summary, x-x.11
```{r}
imdb = imdb[,-c(1,5,28,31,35,58:70)]
```

Step 4: Lets loook at a summary of our data to see what we have in each column. We can see that we have a bunch of NA values so were going to have to deal with those.
```{r}
#summary(imdb)
```
Lets plot these missing values
```{r}
#Missingness graph
library(reshape2)
library(ggplot2)
library(magrittr)
ggplot_missing <- function(x){
  
  x %>% 
    is.na %>%
    melt %>%
    ggplot(data = .,
           aes(x = Var2,
               y = Var1)) +
    geom_raster(aes(fill = value)) +
    scale_fill_grey(name = "",
                    labels = c("Present","Missing")) +
    theme_minimal() + 
    theme(axis.text.x  = element_text(angle=90, vjust=0.5)) + 
    labs(x = "Variables in Dataset with NAs",
         y = "Rows / observations")
}
# Let’s test it out
ggplot_missing(imdb)

#new DF - columsn with NAs
#missings <- subset(imdb, select = c(12,14,57,15,19,30,34,37,53,55))
#ggplot_missing(missings)
```


We have NA Values in:
distributor = 9
director = 3
production_company = 9
director_facebook_likes = 25 
actor_1_star_meter = 6 #dont need
critic_reviews_number = 10 
number_of_faces_in_movie_poster = 7 
movie_budget = 95 #removed them
ratio_movie_cast_likes = 3 
number_of_votes = 23



Step 5: Deal with Na Values
```{r}
#1 distributor - googled values
imdb$distributor = as.character(imdb$distributor)
distibutor <- subset(imdb, is.na(distributor))

imdb$distributor[77] = "Paramount Pictures"
imdb$distributor[212] = "United Artists"
imdb$distributor[256] = "Sony Pictures"
imdb$distributor[483] = "Universal Pictures"
imdb$distributor[858] = "Shochiku Co., Ltd."
imdb$distributor[2341] = "Paramount Pictures"
imdb$distributor[2544] = "Columbia Pictures"
imdb$distributor[2663] = "Relativity Media"
imdb$distributor[3090] = "Missing" # Movie_title = H. Could not find distributor 
imdb$distributor[3105] = "Magnolia Pictures"

attach(imdb)
any(is.na(imdb$distributor))
```

```{r}
#2 director - googled values
imdb$director = as.character(imdb$director)
directors = subset(imdb, is.na(director))

imdb$director[217] = "Peter Deluise"
imdb$director[365] = "Tibor Takics"
imdb$director[2080] = "Mark Steven Johnson" # this one was the date was also in 2003 not 2015

attach(imdb)
any(is.na(imdb$director))
```

```{r}
# 3 prodcution_company - googled values
imdb$production_company = as.character(imdb$production_company)
productionCompany = subset(imdb, is.na(production_company))


imdb$production_company[77] = "Indian Paintbrush"
imdb$production_company[212] = "Selznick International Pictures"
imdb$production_company[256] = "UK Film Council"
imdb$production_company[483] = "Blinding Edge Pictures"
imdb$production_company[858] = " Recorded Picture Company"
imdb$production_company[2341] = "Lakeshore Entertainment"
imdb$production_company[2544] = "Columbia Pictures"
imdb$production_company[2663] = "Relativity Media"
imdb$production_company[3090] = "Missing" # H. 
imdb$production_company[3105] = "Groundswell Productions"

attach(imdb)
any(is.na(imdb$production_company))
```

```{r}
#actor_1_star_meter
imdb$actor_1_star_meter = as.numeric(imdb$actor_1_star_meter)
actor1star = subset(imdb, is.na(imdb$actor_1_star_meter))


imdb$actor_1_star_meter[443] = 2209
imdb$actor_1_star_meter[664] = 5368
imdb$actor_1_star_meter[671] = 5368
imdb$actor_1_star_meter[1494] = 2209
imdb$actor_1_star_meter[1979] = 2209
imdb$actor_1_star_meter[2102] = 5368
imdb$actor_1_star_meter[2304] = 5368
imdb$actor_1_star_meter[2490] = 5368
imdb$actor_1_star_meter[3119] = 5368

attach(imdb)
any(is.na(actor_1_star_meter))
```

```{r}
#number_of_faces_in_movie_poster
imdb$number_of_faces_in_movie_poster = as.numeric(imdb$number_of_faces_in_movie_poster)
faces = subset(imdb, is.na(number_of_faces_in_movie_poster))


imdb$number_of_faces_in_movie_poster[274] = 1
imdb$number_of_faces_in_movie_poster[483] = 0
imdb$number_of_faces_in_movie_poster[529] = 6
imdb$number_of_faces_in_movie_poster[942] = 1
imdb$number_of_faces_in_movie_poster[1600] = 2
imdb$number_of_faces_in_movie_poster[2842] = 4
imdb$number_of_faces_in_movie_poster[2928] = 1

attach(imdb)
any(is.na(number_of_faces_in_movie_poster))
```

```{r}
#movie_budget
imdb$movie_budget = as.numeric(imdb$movie_budget)
budget = subset(imdb, is.na(movie_budget))


imdb$movie_budget[2988] = 1100000
imdb$movie_budget[2989] = 500000
imdb$movie_budget[2990] = 3000000
imdb$movie_budget[2991] = 10000000
imdb$movie_budget[2992] = 30000000
imdb$movie_budget[2993] = 2000000
imdb$movie_budget[2994] = 27000000
imdb$movie_budget[2995] = 5293040
imdb$movie_budget[2996] = 25000000
imdb$movie_budget[2997] = 6000000
imdb = imdb[-which(is.na(imdb$movie_budget)),]

attach(imdb)
any(is.na(movie_budget))
```

```{r}
#ratio_movie_cast_likes
imdb$ratio_movie_cast_likes = as.numeric(imdb$ratio_movie_cast_likes)
ratio = subset(imdb, is.na(ratio_movie_cast_likes))


imdb$ratio_movie_cast_likes[which(is.na(imdb$ratio_movie_cast_likes))] = mean(na.omit(imdb$ratio_movie_cast_likes)) # Replace with the mean

attach(imdb)
any(is.na(ratio_movie_cast_likes))
```

```{r}
#number_of_votes
imdb$number_of_votes = as.numeric(imdb$number_of_votes)
numberofvotes = subset(imdb, is.na(number_of_votes))


imdb$number_of_votes[11] = 6788
imdb$number_of_votes[77] = 54489
imdb$number_of_votes[121] = 747
imdb$number_of_votes[191] = 2878
imdb$number_of_votes[212] = 0
imdb$number_of_votes[256] = 6134
imdb$number_of_votes[393] = 15966
imdb$number_of_votes[483] = 8
imdb$number_of_votes[517] = 2304
imdb$number_of_votes[550] = 7802
imdb$number_of_votes[857] = 64701
imdb$number_of_votes[897] = 75894
imdb$number_of_votes[1601] = 0
imdb$number_of_votes[1650] = 185684
imdb$number_of_votes[1679] = 306331
imdb$number_of_votes[1834] = 23392
imdb$number_of_votes[1953] = 95191
imdb$number_of_votes[1999] = 225660
imdb$number_of_votes[2273] = 99801
imdb$number_of_votes[2429] = 37294
imdb$number_of_votes[2663] = 77611
imdb$number_of_votes[2834] = 439627

attach(imdb)
any(is.na(number_of_votes))
```

```{r}
#critic reviews number
imdb$critic_reviews_number = as.numeric(imdb$critic_reviews_number)
critics = subset(imdb, is.na(critic_reviews_number))


imdb$critic_reviews_number[15] = 0
imdb$critic_reviews_number[53] = 0
imdb$critic_reviews_number[107] = 0
imdb$critic_reviews_number[126] = 0
imdb$critic_reviews_number[274] = 6
imdb$critic_reviews_number[324] = 0
imdb$critic_reviews_number[363] = 0
imdb$critic_reviews_number[1336] = 86

attach(imdb)
any(is.na(critic_reviews_number))
```

```{r}
#duration_number
imdb$duration_mins = as.numeric(imdb$duration_mins)
mins = subset(imdb, is.na(duration_mins))

imdb$duration_mins[2812] = 130

attach(imdb)
any(is.na(imdb$duration_mins))
```

```{r}
imdb[which(is.na(imdb)), ]
imdb = na.omit(imdb)
```

Check if there are any NAs left in the dataset 
```{r}
any(is.na(imdb))
```

Step 7: Make character columns to numeric
```{r}
imdb$user_votes_number = as.numeric(imdb$user_votes_number)
imdb$movie_budget = as.numeric(imdb$movie_budget)
imdb$user_reviews_number = as.numeric(imdb$user_reviews_number)
imdb$actor_2_star_meter = as.numeric(imdb$actor_2_star_meter)
imdb$actor_3_facebook_likes = as.numeric(imdb$actor_3_facebook_likes)
imdb$actor_3_star_meter = as.numeric(imdb$actor_3_star_meter)
imdb$critic_reviews_number = as.numeric(imdb$critic_reviews_number)
imdb$movie_budget = as.numeric(imdb$movie_budget)
imdb$movie_facebook_likes = as.numeric(imdb$movie_facebook_likes)
```

Make factor columns to character 
```{r}
lapply(imdb, class)
imdb$title = as.character(imdb$title)
imdb$actor_1_known_for = as.character(imdb$actor_1_known_for)
imdb$actor_2_known_for = as.character(imdb$actor_2_known_for)
imdb$actor_3_known_for = as.character(imdb$actor_3_known_for)
imdb$director = as.character(imdb$director)
imdb$actor_1_name = as.character(imdb$actor_1_name)
imdb$actor_2_name = as.character(imdb$actor_2_name)
imdb$actor_3_name = as.character(imdb$actor_3_name)
imdb$cinematographer = as.character(imdb$cinematographer)
```
Fix the Color column (has an extra factor)
```{r}
which(imdb$color == "http://www.imdb.com/title/tt0160484/?ref_=fn_tt_tt_1")
imdb$color[which(imdb$color == "http://www.imdb.com/title/tt0160484/?ref_=fn_tt_tt_1")] = "Color"
```

Exploratory Analysis Plots
```{r}
################## Distributions #########################
#For numeric predictors
par(mfrow=c(2,2)) 
plot(duration_mins, imdb_score)
plot(release_year, imdb_score)
plot(aspect_ratio, imdb_score)
plot(number_news_articles, imdb_score)
plot(actor_1_facebook_likes, imdb_score)
plot(actor_1_star_meter, imdb_score)
plot(actor_2_facebook_likes, imdb_score)
plot(actor_2_star_meter, imdb_score)
plot(actor_3_facebook_likes, imdb_score)
plot(actor_3_star_meter, imdb_score)
plot(critic_reviews_number, imdb_score)
plot(user_votes_number, imdb_score)
plot(cast_total_facebook_likes, imdb_score)
plot(number_of_faces_in_movie_poster, imdb_score)
plot(user_reviews_number, imdb_score)
plot(movie_budget, imdb_score)
plot(movie_facebook_likes, imdb_score)
plot(sum_total_likes, imdb_score)
plot(ratio_movie_cast_likes, imdb_score)
plot(movie_meter_IMDB_pro, imdb_score)
plot(number_of_votes, imdb_score)
```


```{r}
##### Bar Chart Distributins #####
par(mfrow=c(2,2))
#director distribution
ggplot(data=imdb , aes(x=director) ) + geom_bar(color = "blue") + ggtitle("Director") + theme(axis.title.x=element_blank()) + theme(axis.text.x = element_text(angle=90))

#release month distribution
ggplot(data=imdb , aes(x=release_month) ) + geom_bar(color = "blue") + ggtitle("Release Months") + theme(axis.title.x=element_blank()) + theme(axis.text.x = element_text(angle=90))

# duration_mins distribution
ggplot(data=imdb , aes(x=duration_mins) ) + geom_bar(color = "blue") + ggtitle("Movie Durations") + theme(axis.title.x=element_blank()) + theme(axis.text.x = element_text(angle=90))

#country distribution
ggplot(data=imdb , aes(x=country) ) + geom_bar(color = "blue") + ggtitle("Countries") + theme(axis.title.x=element_blank()) + theme(axis.text.x = element_text(angle=90))

#content rating distribution
ggplot(data=imdb , aes(x=content_rating) ) + geom_bar(color = "blue") + ggtitle("Content Ratings") + theme(axis.title.x=element_blank()) + theme(axis.text.x = element_text(angle=90))

#distribution of the dependent variable, imdb_score
ggplot(data=imdb , aes(x=imdb_score) ) + geom_bar(color = "blue") + ggtitle("IMDB Scores") + theme(axis.title.x=element_blank()) + theme(axis.text.x = element_text(angle=90))
```

Step 8: Correlation plot between numeric predictors 
```{r}
nums <- unlist(lapply(imdb, is.numeric))  
numericVars = imdb[,nums]
numericVars = numericVars[,-c(19:31)]
corPlot = cor(numericVars)


library(corrplot)
#TODO: change variables names that appear in corrplot
corrplot(corPlot, type = "lower", method = "pie",order = "hclust", 
         tl.col = "black", tl.srt = 25, tl.cex = 0.7)

```
Based off correlation matrix the following variables are significantly correlated: 
 1. number_news_articles and number_of_votes
 2. actor_2_facebook_likes and cast_total_facebook_likes
 3. actor_2_facebook_likes and sum_total_likes 
 4. actor_2_facebook_likes and cast_total_facebook_likes
 5. actor_1_facebook_likes and sum_total_likes 
 6. sum_total_likes and cast_total_facebook_likes 
 7. number_of_faces_in_movie_poster and ratio_movie_cast_likes
 8. movie_facebook_likes and ratio_movie_cast_likes
 9. movie_facebook_likes and number_of_faces_in_movie_poster
Honourable mentions:
 1. imdb_score and duration_mins (0.3)
 2. imdb_score and number_of_votes (0.5)

Outlier Test
```{r}
library(car)
attach(imdb)

Oreg3=lm(imdb_score~duration_mins)
outlierTest(Oreg3) ###2452
imdb=imdb[-c(2452),]
attach(imdb)

Oreg4=lm(imdb_score~aspect_ratio)
outlierTest(Oreg4) ###1495
imdb=imdb[-c(1495),]
attach(imdb)

Oreg5=lm(imdb_score~number_news_articles)
outlierTest(Oreg5) ##860, 1321
imdb=imdb[-c(860,1321),] 
attach(imdb)

Oreg7=lm(imdb_score~director_facebook_likes)
outlierTest(Oreg7) ##642
imdb=imdb[-c(642),]
attach(imdb)


Oreg8=lm(imdb_score~actor_1_facebook_likes)
outlierTest(Oreg8) ##1442
imdb=imdb[-c(1442),]
attach(imdb)

Oreg9=lm(imdb_score~actor_1_star_meter)
outlierTest(Oreg9) ##552
imdb=imdb[-c(552),]
attach(imdb)

Oreg10=lm(imdb_score~actor_2_facebook_likes)
outlierTest(Oreg10) ##2012
imdb=imdb[-c(2012),]
attach(imdb)

Oreg11=lm(imdb_score~actor_2_star_meter)
outlierTest(Oreg11) ##2609
imdb=imdb[-c(2609),]
attach(imdb)

Oreg12=lm(imdb_score~actor_3_facebook_likes)
outlierTest(Oreg12) ##835
imdb=imdb[-c(835),]
attach(imdb)

Oreg13=lm(imdb_score~actor_3_star_meter)
outlierTest(Oreg13) ##1368
imdb=imdb[-c(1368),]
attach(imdb)

Oreg14=lm(imdb_score~critic_reviews_number)
outlierTest(Oreg14) ##1330
imdb=imdb[-c(1330),]
attach(imdb)

Oreg15=lm(imdb_score~user_votes_number)
outlierTest(Oreg15) ##2261
imdb=imdb[-c(2261),]
attach(imdb)

Oreg16=lm(imdb_score~cast_total_facebook_likes)
outlierTest(Oreg16) ##126
imdb=imdb[-c(126),]
attach(imdb)

Oreg17=lm(imdb_score~number_of_faces_in_movie_poster)
outlierTest(Oreg17) ##1645
imdb=imdb[-c(1645),]
attach(imdb)

Oreg18=lm(imdb_score~user_reviews_number)
outlierTest(Oreg18) ##2082
imdb=imdb[-c(2082),]
attach(imdb)

Oreg19=lm(imdb_score~movie_budget)
outlierTest(Oreg19) ##1216
imdb=imdb[-c(1216),]
attach(imdb)

Oreg20=lm(imdb_score~movie_facebook_likes)
outlierTest(Oreg20) ##163
imdb=imdb[-c(163),]
attach(imdb)

Oreg21=lm(imdb_score~sum_total_likes)
outlierTest(Oreg21) ##1575
imdb=imdb[-c(1575),]
attach(imdb)

Oreg22=lm(imdb_score~ratio_movie_cast_likes)
outlierTest(Oreg22) ##375
imdb=imdb[-c(375),]
attach(imdb)

Oreg23=lm(imdb_score~movie_meter_IMDB_pro)
outlierTest(Oreg23) ##2079
imdb=imdb[-c(2079),]
attach(imdb)

Oreg24=lm(imdb_score~number_of_votes)
outlierTest(Oreg24) ##1741
imdb=imdb[-c(1741),]
attach(imdb)
```
Rerun the code to get the numeric dataframe
```{r}
nums <- unlist(lapply(imdb, is.numeric))  
numericVars = imdb[,nums]
numericVars = numericVars[,-c(19:31)]
```


Step 9: Test model 
```{r}
multReg = lm(imdb_score~., data = numericVars)
summary(multReg)
```

Test model using step-wise to get most significant variables 
```{r}
# Step-wise regression
library(MASS)
step.model <- stepAIC(multReg, direction = "both", 
                      trace = FALSE)
summary(step.model)
```

Add in a few categorical variables and test the model
```{r}
#modelSet = imdb[,-c(1,3,10,12,13,15,17,19,21,23,50,51)]
#attach(modelSet)
#multReg1 = lm(imdb_score~ ., data= modelSet)
#summary(multReg1)
```

Bin variables with large number of factors
```{r}
# which columns are factors 
#lapply(imdb, class)
```

Creating bins for director variable
```{r}
#table(imdb$director)
#install.packages("caTools")
library(caTools)
library(boot)

imdb$director_frequency <- table(imdb$director)[imdb$director]
imdb$director_column10 = ifelse(imdb$director_frequency >= 10, imdb$director, 'Other')
imdb$director_column10 = as.factor(imdb$director_column10)
attach(imdb)

dirReg10 = glm(imdb_score~director_column10)
#cv.glm(imdb, dirReg10, K=46)$delta[1]
#summary(dirReg10)

imdb$director_column5 = ifelse(imdb$director_frequency >= 5, imdb$director, 'Other')
imdb$director_column5 = as.factor(imdb$director_column5)
attach(imdb)

dirReg5 = glm(imdb_score~director_column5)
#cv.glm(imdb, dirReg5, K=46)$delta[1]
#summary(dirReg5)

imdb$director_column3 = ifelse(imdb$director_frequency >= 3, imdb$director, 'Other')
imdb$director_column3 = as.factor(imdb$director_column3)
attach(imdb)

dirReg3 = glm(imdb_score~director_column3)
#cv.glm(imdb, dirReg3, K=46)$delta[1]
#summary(dirReg3)

```

```{r}
#install.packages("dplyr")
library(dplyr)

# Creating bins for distributor 
imdb$distributor_freq <- table(imdb$distributor)[imdb$distributor]
imdb$distributor10 = ifelse(imdb$distributor_freq >= 20, imdb$distributor, 'Other')
imdb$distributor10 = as.factor(imdb$distributor10)
attach(imdb)
relevel(imdb$distributor10, ref = "Other")

distReg10 = glm(imdb_score~distributor10)
#cv.glm(imdb, distReg10, K=46)$delta[1]
#summary(distReg10)

# Creating bins for actor 1
imdb$actor1_freq <- table(imdb$actor_1_name)[imdb$actor_1_name]
imdb$actor1_10 = ifelse(imdb$actor1_freq >= 10, imdb$actor_1_name, 'Other')
imdb$actor1_10 = as.factor(imdb$actor1_10)
attach(imdb)
relevel(imdb$actor1_10, ref = "Other")

act1Reg10 = glm(imdb_score~actor1_10)
#cv.glm(imdb, act1Reg10, K=46)$delta[1]
#summary(act1Reg10)

# bins for actor 2
imdb$actor2_freq <- table(imdb$actor_2_name)[imdb$actor_2_name]
imdb$actor2_10 = ifelse(imdb$actor2_freq >= 7, imdb$actor_2_name, 'Other')
imdb$actor2_10 = as.factor(imdb$actor2_10)
attach(imdb)
relevel(imdb$actor2_10, ref = "Other")

act2Reg10 = glm(imdb_score~actor2_10)
#cv.glm(imdb, act2Reg10, K=46)$delta[1]
#summary(act2Reg10)

# bins for actor 3
imdb$actor3_freq <- table(imdb$actor_3_name)[imdb$actor_3_name]
imdb$actor3_10 = ifelse(imdb$actor3_freq >= 5, imdb$actor_3_name, 'Other')
imdb$actor3_10 = as.factor(imdb$actor3_10)
attach(imdb)
relevel(imdb$actor3_10, ref = "Other")

act3Reg10 = glm(imdb_score~actor3_10)
#cv.glm(imdb, act3Reg10, K=46)$delta[1]
#summary(act3Reg10)

# binning cinematographer 
imdb$cin_freq <- table(imdb$cinematographer)[imdb$cinematographer]
imdb$cinematographer10 = ifelse(imdb$cin_freq >= 15, imdb$cinematographer, 'Other')
imdb$cinematographer10 = ifelse(imdb$cinematographer10 == "multiple", 'Other',imdb$cinematographer10)
imdb$cinematographer10 = as.factor(imdb$cinematographer10)
attach(imdb)
relevel(imdb$cinematographer10, ref = "Other")

cinReg10 = glm(imdb_score~cinematographer10)
#cv.glm(imdb, cinReg10, K=46)$delta[1]
#summary(cinReg10)

# binning production co 
imdb$prod_freq <- table(imdb$production_company)[imdb$production_company]
imdb$prod10 = ifelse(imdb$prod_freq >= 20, imdb$production_company, 'Other')
imdb$prod10 = as.factor(imdb$prod10)
attach(imdb)
relevel(imdb$prod10, ref = "Other")

prodReg10 = glm(imdb_score~prod10)
#cv.glm(imdb, prodReg10, K=46)$delta[1]
#summary(prodReg10)

# changing aspect ratio to a factor
imdb$aspect_ratio = as.factor(imdb$aspect_ratio)
attach(imdb)
aspectReg10 = lm(imdb_score~aspect_ratio)
summary(aspectReg10)

# binning country 
imdb$country = as.character(imdb$country)
imdb$country_freq <- table(imdb$country)[imdb$country]
imdb$country10 = ifelse(imdb$country_freq >= 20, imdb$country, 'Other')
imdb$country10 = as.factor(imdb$country10)
attach(imdb)
relevel(imdb$country10, ref = "Other")

countryReg10 = glm(imdb_score~country10)
#cv.glm(imdb, countryReg10, K=46)$delta[1]
#summary(countryReg10)

#binning content rating
imdb$contentRating_freq <- table(imdb$content_rating)[imdb$content_rating]
imdb$content_rating = as.character(imdb$content_rating)
imdb$content10 = ifelse(imdb$contentRating_freq >= 50,imdb$content_rating,"Other")
imdb$content10 = as.factor(imdb$content10)
attach(imdb)
relevel(imdb$content10, ref = "Other")
```

Testing categorial variables in a model using step-wise 
```{r}
categoricalVar = imdb[,c(3,6:9,53,57,59,61,63,65,67,69)]
catReg = lm(imdb_score~.,data=categoricalVar)
#summary(catReg)

library(MASS)
catStep <- stepAIC(catReg, direction = "both", 
                      trace = FALSE)
#summary(catStep)
```

Combine numeric and categorical variables 
```{r}
predictors = c(2,5,54) # duration, director 
predictorSet = imdb[,predictors]

comboReg = glm(imdb_score~poly(duration_mins,2)+director_column10,data=predictorSet)
cv.glm(imdb, comboReg, K=46)$delta[1] #MSE=0.9057
#summary(comboReg)

predictor2 = c(2,5,34,37,39,42,45,54) # with genre
predictorSet2 = imdb[,predictor2]

comboReg2 = glm(imdb_score~poly(duration_mins,2)+director_column10+action+thriller+romance+horror+drama+animation,data=predictorSet2)
cv.glm(imdb, comboReg2, K=46)$delta[1] #MSE=.8266
#summary(comboReg2)


predictor3 = c(2,5,54,60) # duration, actor_1, director
predictorSet3 = imdb[,predictor3]

comboReg3 = glm(imdb_score~poly(duration_mins,2)+director_column10+actor1_10,data=predictorSet3)
cv.glm(imdb, comboReg3, K=46)$delta[1] #MSE= 0.9031
#summary(comboReg3)

predictor4 = c(2,5,54,58,60) # duration, actor_1, director, distributor 
predictorSet4 = imdb[,predictor4]


comboReg4 = glm(imdb_score~poly(duration_mins,2)+director_column10+actor1_10+distributor10,data=predictorSet4)
cv.glm(imdb, comboReg4, K=46)$delta[1] #MSE= 0.8775
#summary(comboReg4)


predictor5 = c(2,5,58,60) # duration, actor_1, distributor 
predictorSet5 = imdb[,predictor5]

comboReg5 = glm(imdb_score~poly(duration_mins,2)+actor1_10+distributor10,data=predictorSet5)
cv.glm(imdb, comboReg5, K=46)$delta[1] #MSE= 0.8775


predictor6 = c(2,5,50,54,58,60) # duration, director, actor_1, distributor, number_of_votes
predictorSet6 = imdb[,predictor6]

comboReg6 = glm(imdb_score~poly(duration_mins,2)+poly(number_of_votes,3)+director_column10+actor1_10+distributor10,data=predictorSet6)
cv.glm(imdb, comboReg6, K=46)$delta[1] #MSE= 0.6942
#summary(comboReg6)

predictor7 = c(2,5,13,50,54,58,60) # duration, director, actor_1, director_fb_likes, distributor, number_of_votes
predictorSet7 = imdb[,predictor7]

comboReg7 = glm(imdb_score~poly(duration_mins,2)+poly(number_of_votes,3)+poly(director_facebook_likes,4)+director_column10+actor1_10+distributor10,data=predictorSet7)
cv.glm(imdb, comboReg7, K=46)$delta[1] #MSE= 0.6928
#summary(comboReg7)

predictor8 = c(2,5,13,54,58,60) # duration, director, actor_1, director_fb_likes, distributor
predictorSet8 = imdb[,predictor8]

comboReg8 = glm(imdb_score~poly(duration_mins,2)+poly(director_facebook_likes,4)+director_column10+actor1_10+distributor10,data=predictorSet8)
cv.glm(imdb, comboReg8, K=52)$delta[1] #MSE= 0.8625
#summary(comboReg8)

predictor9 = c(2,5,13,54,58,60,68) # duration, director, actor_1, director_fb_likes, distributor, production company
predictorSet9 = imdb[,predictor9]

comboReg9 = glm(imdb_score~poly(duration_mins,2)+poly(director_facebook_likes,4)+director_column10+actor1_10+distributor10+prod10,data=predictorSet9)
cv.glm(imdb, comboReg9, K=52)$delta[1] #MSE= 0.8657
#summary(comboReg9)

predictor10 = c(2,5,8,13,54,58,60) # duration, director, actor_1, director_fb_likes, distributor, content_rating
predictorSet10 = imdb[,predictor10]

comboReg10 = glm(imdb_score~poly(duration_mins,2)+poly(director_facebook_likes,4)+director_column10+actor1_10+distributor10,data=predictorSet10)
cv.glm(imdb, comboReg10, K=52)$delta[1] #MSE= 0.8637
#summary(comboReg8)

comboReg10.1 = glm(imdb_score~poly(duration_mins,2)+poly(director_facebook_likes,4)+director_column10+actor1_10+distributor10,data=predictorSet10)
summary(comboReg10.1)# adj. R^2 
cv.glm(imdb, comboReg10.1, K=52)$delta[1] 

predictor11 = c(2,4,5,13,54,58,60) # release_year, duration, director, actor_1, director_fb_likes, distributor
predictorSet11 = imdb[,predictor11]

comboReg11 = glm(imdb_score~poly(release_year,2)+poly(duration_mins,2)+poly(director_facebook_likes,4)+director_column10+actor1_10+distributor10,data=predictorSet11)
cv.glm(imdb, comboReg11, K=52)$delta[1] #MSE= 0.8343
summary(comboReg11)

predictor12 = c(2,4,5,13,43,54,58,60) # release_year, duration, director, drama, actor_1, director_fb_likes, distributor
predictorSet12 = imdb[,predictor12]

comboReg12 = glm(imdb_score~poly(release_year,2)+poly(duration_mins,2)+poly(director_facebook_likes,4)+director_column10+actor1_10+distributor10,data=predictorSet12)
cv.glm(imdb, comboReg12, K=52)$delta[1] #MSE= 0.8366
#summary(comboReg12)


predictor13 = c(2,4,5,13,54,58,60,66) # release_year, duration, director, actor_1, director_fb_likes, distributor, cinematographer
predictorSet13 = imdb[,predictor13]

comboReg13 = glm(imdb_score~poly(release_year,2)+poly(duration_mins,2)+poly(director_facebook_likes,4)+director_column10+actor1_10+distributor10,data=predictorSet13)
cv.glm(imdb, comboReg13, K=52)$delta[1] #MSE= 0.8345
#summary(comboReg13)

```

Best Model
```{r}
newest = glm(imdb_score~poly(duration_mins,2)+director_column10+action+thriller+romance+horror+drama+animation+distributor10+number_of_faces_in_movie_poster+color+musical+content10, data=imdb)

cv.glm(imdb, newest, K=46)$delta[1] 
#summary(comboS)

######## residual plots #########
#residualPlots(comboS) #We can see that ratio_movie cast likes, movie_fb_likes are non-linear so we made them into polynomials with degree 2


########## heteroskedasticity #########
library(car)
# lm model
newest.lm = lm(imdb_score~poly(duration_mins,2)+director_column10+action+thriller+romance+horror+drama+animation+distributor10+number_of_faces_in_movie_poster+color+musical+content10, data=imdb)

#ncvTest
ncvTest(newest.lm)
plot(predict(newest.lm), residuals(newest.lm), col="red")
abline(0,0,lty = 2)

library(sandwich)
library(lmtest)
library(plm)
#adjusting for hetero
coeftest(newest.lm, vcov. = vcovHC(newest.lm, type = "HC1"))
summary(newest.lm)

########## collinarity test ###########
library(olsrr)
ols_coll_diag(newest.lm)

```

Relevelling factors so Other is the reference/first factor variable 
```{r}
relevel(imdb$director_column10, ref = "Other")
relevel(imdb$distributor10, ref = "Other")
relevel(imdb$content10, ref = "Other")
attach(imdb)
newest.lm = lm(imdb_score~poly(duration_mins,2)+director_column10+action+thriller+romance+horror+drama+animation+distributor10+number_of_faces_in_movie_poster+color+musical+content10, data=imdb)
summary(newest.lm)

library(stargazer)
stargazer(newest.lm, type="html", title = "Our Best Model", out="./stargazertable.html")
#summary(newest)
```

Predictions
```{r}
##########################
newest = glm(imdb_score~poly(duration_mins,2)+director_column10+action+thriller+romance+horror+drama+animation+distributor10+number_of_faces_in_movie_poster+color+musical+content10, data=imdb)

cv.glm(imdb, newest, K=52)$delta[1] #MSE= ~.781

#Predicting The Grinch 
predict(newest, data.frame(duration_mins=105, director_column10="Other", action = 0, thriller=0,romance=0,horror=0,drama = 0, animation=1,distributor10="Universal Pictures",number_of_faces_in_movie_poster=2, color="Color",musical=0,content10="PG")) # Rating = 6.92818

#Predicting Postcards From London
predict(newest, data.frame(duration_mins=90, director_column10="Other", action = 0, thriller=0,romance=0,horror=0,drama = 1, animation=0, distributor10="Other",number_of_faces_in_movie_poster=5, color="Color",musical=0,content10="Other")) # Rating = 6.440592

#Predicting The Long Dumb Road
predict(newest, data.frame(duration_mins=90, director_column10="Other", action = 0, thriller=0,romance=0,horror=0,drama =0, animation=0, distributor10="Universal Pictures",number_of_faces_in_movie_poster=2,
color="Color",musical=0,content10="R")) #Rating = 6.248

#Predicting Instant Family
predict(newest, data.frame(duration_mins=90, director_column10="Other", action = 0, thriller=0,romance=0,horror=0,drama =0, animation=0, distributor10="Paramount Pictures",number_of_faces_in_movie_poster=5,
color="Color",musical=0,content10="PG-13")) # Rating = 5.876

#Predicting Crimes of Grindelwald
predict(newest, data.frame(duration_mins=134, director_column10="Other", action = 0, thriller=0,romance=0,horror=0,drama = 1, animation=0, distributor10="Warner Bros.",number_of_faces_in_movie_poster=10,
color="Color",musical=0,content10="PG-13")) #Rating = 6.68

#Predicting The Clovehitch Killer
predict(newest, data.frame(duration_mins=110, director_column10="Other", action = 0, thriller=0,romance=0,horror=1,drama = 1, animation=0, distributor10="Other",number_of_faces_in_movie_poster=1,
color="Color",musical=0,content10="Other")) #Rating = 6.661

#Predicting Robin Hood
predict(newest, data.frame(duration_mins=116, director_column10="Other", action = 1, thriller=0,romance=0,horror=0,drama = 0, animation=0, distributor10="Lionsgate",number_of_faces_in_movie_poster=6,
color="Color",musical=0,content10="PG-13")) #Rating = 5.879733

#Predicting Creed 2
predict(newest, data.frame(duration_mins=90, director_column10="Robert Zemeckis", action = 0, thriller=0,romance=0,horror=0,drama = 1, animation=0, distributor10="Universal Pictures",number_of_faces_in_movie_poster=1,
color="Color",musical=0,content10="PG-13")) #Rating = 6.765665

#Predicting The Welcome to Warwen
predict(newest, data.frame(duration_mins=133, director_column10="Other", action = 0, thriller=0,romance=0,horror=0,drama = 1, animation=0, distributor10="Warner Bros.",number_of_faces_in_movie_poster=1,
color="Color",musical=0,content10="PG-13")) # Prediction = 7.040479

#Predicting Ralph Breaks the Internet
predict(newest, data.frame(duration_mins=112, director_column10="Other", action = 0, thriller=0,romance=0,horror=0,drama = 0, animation=1, distributor10="Walt Disney Studios Motion Pictures",number_of_faces_in_movie_poster= 0,
color="Color",musical=0,content10="PG")) #Rating = 7.505993
#seems like the 78 faces is fucking this up.

#Predicting Second Act
predict(newest, data.frame(duration_mins=105, director_column10= "Other", action = 0, thriller=0,romance=1,horror=0,drama = 0, animation=0, distributor10="Other",number_of_faces_in_movie_poster= 1, color="Color",musical=0,content10="PG-13")) #Rating = 6.108134

#Predicting Becoming Astrid
predict(newest, data.frame(duration_mins=124, director_column10="Other", action = 0, thriller=0,romance=0,horror=0, drama = 1, animation=0, distributor10="Other",number_of_faces_in_movie_poster=2,
color="Color",musical=0,content10="Other")) #Rating = 7.220898

```

Residual Plots for "newest" model 
```{r}
residualPlots(newest)
```

